A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Treat year as categorical variable

modelsummary::datasummary_balance(formula = ~ sex, data = dat_clean, dinm = FALSE)

>>>>

within(dat, {
  sex[is.na(sex)] <- "unknown"
  year <- as.factor(year) # Year is more interesting if analyzed as factor
}) |>
  (\(x) { # Add number of non-missings
    idx <- which(sapply(x, is.numeric))
    n <- sapply(x, \(v) sum(!is.na(v)))
    names(x) <- names(x) |>
      replace(
        list = idx,
        values = paste0(names(x), " (N=", n, ")")[idx]
      )
    x
  })() |>
  modelsummary::datasummary_balance(formula = ~ sex, dinm = FALSE) |>
  tinytable::style_tt(
    # Make table more compact to fit on page
    tabularray_inner = "rowsep={0.2em}, colsep = {0.2em}"
  )
